\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent02-12-2014\\
 
\noindent Dear Intuit Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my
Master's degree in Computer Science. I am applying for the position of Software Engineer
recently posted in yours Careers website and I am confident that my unique skill set make me an ideal candidate for the position.\\

I am a Research Assistant at Vision and Perpetual machines lab where we work on interesting research problems on
Machine Learning and Data Mining. I have worked on many state of the art research projects, one of my
project called "Jake" is an in house computer vision library which is soon to released as an
open source project. I have coded modules like Object Detection and Tripartite graph. The whole library
is coded in C++ along with STL and Boost. This project gave me a deeper understanding in managing large code bases, working with Unix environment and experience towards using STL and Boost. I am a supporter of Open Source and 
Linux is my primary operating system. I usually code in Java, Python or C++ and most of my projects are in my Github(sbondada) account. I have also been to many hackathons.
One of my project we developed in UB Hacking called "Spoddit" was appreciated as one of the most professional looking website. The back end
was coded in python while Java script, HTML and CSS for its front end. Working as a research assistant and being a part of many projects, I
gained valuable experience toward Software Engineering design and OOP concepts. I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation
and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to
discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

