\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.209, Postbox.no.9\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent01-19-2014\\
 
\noindent Dear Peak Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science. I am applying
for the position of Software Engineer (Entrylevel) recently posted  in Glassdoor and I am confident that my unique skill set would
make me an ideal candidate for the position.\\

I have been working as an Research Assistant at Vision and Perpetual machine lab on some state of the art research  projects which required strong
analytical ability.Jake is an example of such project which is a Computer Vision Library which was in the development phase for a year now.I have been working on this and contributed several modules. We are going to realease the library as an open source in summer of 2014. I have worked mostly in a Collabrative
team environment using most of the open source tools like Git for versioning,Vim as an editor, Ubuntu as my primary Operating system and many
more. I have also been using java in many of my projects. I have coded a Complete query evaluation engine for one my course projects. The
project was little daunting earlier but was able to finish the project just with a little direct oversight.\\
 
I like to code with a perpective of improving our society or with a focus on customer, I assure you that my expertise combined with my motivation
and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to
discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

