\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent01-22-2014\\
 
\noindent Dear Mathworks Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science. I am
applying
for the position of Application Support Engineers recently posted in your career site and I am confident that my unique skill set
make me an ideal candidate for the position.\\

I have coded various projects and participated in hackathons.Most of my projects are coded in java or C++ and all are open sourced and
committed to my github(sbondada) account. I have recently developed a website called Spoddit. It is a music play list generator based on the
recent song collections posted on some popular subreddits of Reddit. The front end was designed as simple as possible and in perspective of the
user. Its been
appreciated as the most professional looking website in Ub Hacking. I am also a Research Assistant at VPML lab where we work as a team and collaborate. I have worked on "Jake", a computer vision
library where I have coded object detection and video feature module in C++. This experience helped me understand Full life cycle application development. I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation
and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to
discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

