\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent01-18-2014\\
 
\noindent Dear ZipRecruiter Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science. I am applying
for the position of Entry-Level Software Engineer recently posted in Glassdoor.com and I am confident that my unique skill set
make me an ideal candidate for the position.\\

I have been involved with various projects, research and hackathons. One of the projects which we implemented is "whereIsIt",which involved
lots of web page spidering and parsing. This project involved crawling sites like Reddit and parse the data for places and images, which would then be used for
extraction of information in JSON objects from a series of API's and websites.I have been working with Ubuntu as my primary operating system 
and I have written scripts to process text for my projects using unix commands. I have also worked on constructing a whole query evaluation
engine which involved in depth learning of the functionality of sql query and improving the evaluation plans for the SQL queries which improved
my understanding of SQL commands. I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation
and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to
discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

