\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent02-16-2014\\
 
\noindent Dear WalmartLabs Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science and
specializing in Artificial Intelligence. I am applying for the position of Data Scientist posted in yours Careers website and I am confident
that my unique skill set would make me an ideal candidate for the position.\\

I am a Research Assistant at Vision and Perpetual machines lab where we work on interesting research problems related to Computer
Vision, Machine Learning and Data Mining. I have worked on many state of the art research projects, one of my active project called "Simplest Action
Descriptors using Bounded Dense Trajectories" is coded completely in python and is in Github. The project is about finding the simplest action descriptor
for Action Recognition with dense trajectories using SVM and chi square kernel for action recognition. I gained deeper understanding of the
usage of kernels, feature computation and classification in the pursuit of identifying the simpler action descriptors. I am a supporter of Open Source and Linux is my primary operating system. I usually code in Java, Python or C++ and most of my projects are in my Github(sbondada) account. 
I have also constructed a query evaluation engine for SQL using tree based optimization for evaluation plan generation. This project helped me understand the fundamental concepts
of relational databases and ace my database course. I am seeking to complement this experience with a full time position at your reputed company that will help lay the 
groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

