\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent01-27-2014\\
 
\noindent Dear IXL Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science. I am applying
for the position of Software Engineer - New Grad recently posted on your website and I am confident that my skill set would make me an ideal candidate for the position.\\

I am a Research Assistant at Vision and Perpetual Machines lab, we work on research problems related to Computer Vision and  Machine
learning. I have coded many state of the art project like Video2Text, Jake and Automatic graph learning. I have worked in many different
teams as well as Individually on my projects. I usually code in Java, Python or C++ and most of my projects are in my Github (sbondada). I consider sharing is the only way of learning and technology can help
in improving the education further. I am a primary user of Linux and a supporter of open source. I have been to many Hackathons. One of my
projects called Spoddit has been considered as most professional looking website in UB Hacking. The whole back end was written in python with
CSS, Java Script and HTML used for its front end. I have also constructed a query evaluation engine for SQL in my Database course coded in Java. It was
one of the toughest projects, involving of construction of a efficient evaluation plan for each command. This Project improved my
Understanding of Object Oriented language and problem solving skills. 
I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a
successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

