\documentclass[10pt,letterpaper,oneside]{article} \usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent02-06-2014\\
 
\noindent Dear Yelp Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science. I am
applying for the position of Software Engineer - Back End posted in yours Careers website and I am confident that my unique skill set make me an ideal candidate for the position.\\

I am a Research Assistant at Vision and Perpetual machines lab where we work on interesting research problems on Computer Vision and Machine
Learning. I have been to many hackathons. One of the project which gave significant appreciation for its professional looks
at UB Hacking was "Spoddit". This is a website for music enthusiast, where the system periodically crawls Reddit for 
recently posted songs and provide direct play links and also allows you to export play lists directly to your Spotify account. The whole back end was 
written in python and we used CSS, HTML, Javascript for its front end. we mostly used open source tools except for the logo design and also
released the code of our website. I am a supporter of Open Source and a avid user of Linux. I like to build systems which are simple and
useful to people. 
I usually code in Python, Java or C++ and most of my projects are in my Github(sbondada) account. 
I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

