\documentclass[10pt,letterpaper,oneside]{article}
\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in]{geometry}   
\marginparwidth=0pt
\marginparsep=0pt
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{pag}
\usepackage[usenames,dvipsnames]{color}
\begin{document}
\noindent 1400 Millersport Highway,\\
Apt.no.210, Postbox.no.10\\
Buffalo, New York, USA-14221\\
sbondada@buffalo.edu\\
www.kaushalbondada.me\\
(716) 622-8639\\

\noindent02-02-2014\\
 
\noindent Dear eBay Representative,\\
 
I am a graduate student at the University at Buffalo, State University of New York, pursuing my Master's degree in Computer Science and
specializing in Artificial Intelligence. I am applying for the position of Software Engineer Back End recently posted in yours Careers website and I am confident that my unique skill set make me an ideal candidate for the position.\\

I am a Research Assistant at Vision and Perpetual machines lab where we work on interesting research problems on Computer
Vision, Machine Learning and Data Mining. I have worked on many state of the art research projects, one of my active project called
"Video2Text" is a website which converts the semantic information embedded in the visual part of the video to text. We used Data mining for the
domain discovery, Computer Vision for object detection and language models in NLP for sentence generation. I have coded one of the pipeline
for the system in C++ and is actively being used by others as a REST API.I am a supporter of Open Source and Linux is my primary operating
system. I usually code in Java,Python or C++ and most of my projects are in my Github(sbondada) account. I have also been to many hackathons.
One of my project we developed in UB Hacking called "Spoddit" was appreciated as one of the most professional looking website. The back end
was coded in python and Java script, HTML and CSS for its front end. Working as a research assistant and being a part of many projects, I
had a deeper understanding toward Data Structures, Algorithms ,Software Engineering and OOP concepts. I am seeking to complement this experience with a full time position at your reputed company that will help lay the groundwork for a successful career in software industry.\\

I bring along with me passion and commitment to work, I assure you that my expertise combined with my motivation
and enthusiasm will make me an asset to your department. I thank you in advance for reviewing my application and I would be more than glad to
discuss further about this position. Feel free to contact me anytime at (716) 622-8639 or sbondada@buffalo.edu. I have enclosed my resume for your review and I look forward to hearing from you.\\
 
\noindent Sincerely,\\
Srinivasa Sai Kaushal Bondada\\
Enclosure: Resume\\

\end{document}

